State and Input Dependent Disturbances in Min-Max Model Predictive Control

### 2015-11-02 draft.tex
Daily changes.
what happened

[ticket: X]

Robust model predictive control (RMPC) methods compute control laws for uncertain systems that optimise a 
performance criterion for all possible realisations of the uncertainties.
%
One major challenge in RMPC is to guarantee feasibility of the problem for all possible uncertainties in 
presence of state constraints.
%
This can be achieved by introducing specifically designed constraints in such a way that at the
end of the control horizon the system state is contained in a set that is feasible and invariant for all
possible realisations of uncertainty and for a given feedback controller, in particular the largest such set, 
the so called \emph{maximal robust positive invariant} (MRPI) set.
%
Although this concept was introduced shortly after Witsenhausen proposed the use of a game theoretic approach
to robust model predictive control in~\cite{Witsenhausen:1968} by several authors~\cite{Bertsekas:1971,Glover:1971},
it took over two decades before the first MRPI sets could be algorithmically determined.

>>>>

Robust model predictive control (RMPC) methods compute control laws for uncertain systems that optimise a 
performance criterion for all possible realisations of the uncertainties.
%
One major challenge in RMPC is to guarantee feasibility of the problem for all possible uncertainties in 
presence of state constraints.
%
This can be achieved by introducing specifically designed constraints in such a way that at the
end of the control horizon the system state is contained in a set that is feasible and invariant for all
possible realisations of uncertainty and for a given feedback controller, in particular the largest such set, 
the so called \emph{maximal robust positive invariant} (MRPI) set.
%
Although this concept was introduced shortly after Witsenhausen proposed the use of a game theoretic approach
to robust model predictive control in~\cite{Witsenhausen:1968} by several authors~\cite{Bertsekas:1971,Glover:1971},
it took over two decades before the first MRPI sets could be algorithmically determined explicitly.
%
The main contribution of this paper is to discuss the use of parametrised sets to model uncertainties, as a parameter
we use the state and the input allowing us to model linearisation errors and multiplicative uncertainties in an 
additive way.
%
We develop the abstract and computational tools necessary to characterise and determine these sets, we introduce the 
concept of \emph{parametric convexity} which is essential in order to obtain convex MRPI and controllable sets.

The algorithmic solution of RMPC problems suffered a similar history as the MRPI sets did,
